OpenMotion: An open source library for attitude estimation.

### 2016-05-20 Article/state_of_the_art.tex
modif results simulation

>>>>

From figures \ref{histo_s1_add} et \ref{histo_s2_add}, we can observe that USQUE has the best score $s_1$, which proove its effectiveness in term of accuracy. While CGO has the highest $s_2$, that make it more interesting for embedded system context. On a other hand, it seems that PF is not as accurate as expected. This is due to the fact that its covariance time requirement is more important than USQUE. Moreover, as shown in figure \ref{error_plot}, even when the noise is strong, PF become more reliable than USQUE after a fex second of utilization. \\

\begin{figure}
\centering
\includegraphics[scale=0.3]{images/error_plot.png}
\caption{Plot of the RMS attitude error (score $s_1$)over time when the noise is AWGN with strong strength. Here only PF, USQUE and CGO is represented. We can observe that PF and CGO require more time to converge to the solution. However, after a few second, PF become more reliable than USQUE. }
\label{error_plot}
\end{figure}
